Compare with and without expansion

### 2024-08-12 Rmd/compare_with_and_without_expansion.Rmd
run and plot ISS using Steve's y2 object containing all the data for single sex. Use Cruise as placeholder for Trip for foreign data for now.

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "ISS", xlab = "year", cex.lab = 1.3, ylim = c(0, max(out2$iss_length$iss)*1.1)) 
lines(out2$iss_length$YEAR, out2$iss_length$iss, col = "blue")
legend("topleft", lty = c(1,1), col = c("black", "blue"), legend = c("with expansion", "without expansion"))

>>>>

plot(out1$iss_length$YEAR, out1$iss_length$iss, type = "l", ylab = "Sample Size", xlab = "year", cex.lab = 1.3, ylim = c(0, max(out2$iss_length$nss)*1.1)) 
lines(out2$iss_length$YEAR, out2$iss_length$iss, col = "blue")
lines(out2$iss_length$YEAR, out2$iss_length$nss, col = "orange")
legend("topright", lty = c(1,1,1), col = c("orange", "black", "blue"), legend = c("nominal", "with expansion", "without expansion"))
